Hardware-in-Loop Plant Modeling for Autonomous Vehicle

### 2021-10-07 proposalPres.tex
Updated presentation slides, system level requirement document

\title[HIL Plant Modeling (Proposal)]{HIL Plant Modeling}

% % A subtitle is optional and this may be deleted
\subtitle{Product Proposal}

\author[K.~Allen, D.~Beebe, J.~Braker]{Kallistah~Allen \and Darrah~Beebe \and
Jason~Braker
Advisors:~Dr.~Suruz~Miah \and Dr.~Prasad~Shastry}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

\begin{frame}{Introduction}
  % \begin{center}
  %   % \href{videos/proposalVideo.mp4}{\includegraphics[width=0.8\textwidth]{figs/img/proposalVideoTitle}}
  % \end{center}
  % \begin{center}
  %   \includemedia[
  %     width=\textwidth,
  %     height=0.7\textheight,
  %     label=proposalVideo,
  %     % activate=onclick,
  %     % playbutton=fancy,
  %     addresource=videos/proposalVideo.mp4,
  %     flashvars={source=videos/proposalVideo.mp4}]
  %     {}{VPlayer.swf}
  %     \\
  %     % \mediabutton[
  %     %   mediacommand=proposalVideo:playPause,
  %     %   overface=\color{blue}{\fbox{\strut \faPause\ \faPlay}},
  %     %   downface=\color{red}{\fbox{\strut \faPause\ \faPlay}}
  %     % ]{}
  %     % \mediabutton[
  %     %   mediacommand=proposalVideo:setSource
  %     %   [(videos/proposalVideo.mp4)]]{\fbox{Introduction Video}}
  % \end{center}
\end{frame}

\begin{frame}{Problem Statement}
  \begin{block}{Problem Statement}
    \begin{LARGE}
      Model vehicle subsystems for a Lexus platform. 
    \end{LARGE}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{LARGE}
      Use the System Identification Toolbox in Matlab to develop a model for each subsystem. 
    \end{LARGE}
  \end{block}
\end{frame}

% \begin{frame}{Introduction}{}
% %\documentclass{beamer}
%   % applications of mobile robot navigation and problem description
%   \begin{block}{Applications of Mobile Carts}
%     \begin{itemize}
%       %\item Mail delivery
%       %\item Transferring files in offices
%       \item Carrying medical supplies in hospitals (Fig.\ref{fig:medCart})
%       \item Carrying materials and tools in factories (Fig. \ref{fig:factCart})
%       \item Shopping carts for ease of use and people with disabilities
%     \end{itemize}
%   \end{block}
%       \begin{figure}
%       \centering
%       \begin{minipage}[t]{0.5\textwidth}
%         \centering
%         \includegraphics[height=3.0cm]{figs/img/MedicalRoboticCart}
%         \caption{Medical Mobile Robotic Cart\textsuperscript{a}}
%         \label{fig:medCart}
%       \end{minipage}
%       \begin{minipage}[t]{0.4\textwidth}
%         \centering
%         \includegraphics[height=2.0cm]{figs/img/FactoryRoboticCart}
%         \caption{Factory Mobile Robotic Cart\textsuperscript{b}}
%         \label{fig:factCart}
%       \end{minipage}
%       \end{figure}
%     \begin{tiny}
%       \textsuperscript{a}https://www.cnet.com/news/robots-give-a-helping-hand-in-san-franciscos-newest-hospital/\\\textsuperscript{b}https://www.greencarcongress.com/2020/05/20200515-nvidia.html
%     \end{tiny}
% \end{frame}

@@

\begin{frame}{Literature Review}
  \begin{block}{Existing Solution}
        Mobile platform interface with ultrasound and radio transmission technology~\cite{Sales2016-CompaRob}
  \end{block}
    % \begin{figure}[b]
    %     \centering
    %     \includegraphics[width=0.45\textwidth]{figs/img/CompaRob}
    %     \caption{CompaRob}
    %     %\label{fig:sysBlockDiag}
    % \end{figure}
\end{frame}

@@

\begin{frame}{Existing Solutions}
  \begin{block}{Problems}
    \begin{itemize}
      \item Require line-of-sight between robot and user
      \item Some require costly dedicated image processing hardware
    \end{itemize}
  \end{block}
  \pause
  \begin{block}{Benefits of Proposed Solution}
    \begin{itemize}
      \item Line-of-sight is not required since analog RF signals will be used
      \item RF components are cost-effective
    \end{itemize}
  \end{block}
\end{frame}

@@

\section{System Requirements}
\begin{frame}{System Requirements}
  \begin{block}{Specifications}
    \begin{itemize}
      \item Cart should be able to follow the remote target
      \item Cart should maintain a distance of 1~[\si{\meter}] to 1.5~[\si{\meter}] from the remote target.
      \item Cart should be able to attain a speed of at least 1~[\si{\meter\per\second}]
      \item Cart should not require line-of-sight to follow remote
     \end{itemize}
  \end{block}
\end{frame}

@@

\section{Concluding Remarks}
\begin{frame}{Concluding Remarks}
  \begin{block}{Project goals}
    \begin{LARGE}
      \begin{itemize}
        \item Develop a robotic cart system utilizing wireless signal strength to locate and follow the user.
        \begin{itemize}
          \item Does not require line-of-sight
          \item Low-cost design
        \end{itemize}
      \end{itemize}
    \end{LARGE}
  \end{block}
  \begin{block}{Anticipated Challenges}
    \begin{itemize}
      \item Inaccurate distance measurements due to multipath effect from environment
      \item Achieving full 360\textdegree measurement in short enough time
    \end{itemize}
  \end{block}
\end{frame}

@@

% \begin{frame}{References}
%   \bibliographystyle{IEEEtran}
%   \begin{itemize}
%     \item N. Rawashdeh, R. Haddad, O. Jadallah, and A. To’ma, “A person-following
% robotic cart controlled via a smartphone application: design and evaluation,”
% 09 2017, pp. 1–5.
%     \item M. M. Islam, A. Lam, H. Fukuda, Y. Kobayashi, and Y. Kuno, “An intelligent
% shopping support robot: understanding shopping behavior from 2d skeleton data using gru network,” ROBOMECH Journal, vol. 6, no. 1, 2019.
%     \item J. Sales, J. Marti, R. Marin Prades, E. Cervera, and P. Sanz, “Comparob: The
% shopping cart assistance robot,” International Journal of Distributed Sensor Networks, vol. 2016, pp. 1–15, 02 2016.
%     \item M. S. Miah, J. Knoll, and K. Hevrdejs, “Intelligent range-only mapping and navigation for mobile robots,” IEEE Transactions on Industrial Informatics, vol. 14, no. 3, pp. 1164–1174, 2018.
%     \item D. Li and S. Lane, “A novel and versatile parabolic reflector that significantly
% improves wi-fi reception at different distances and angles,” 2013.

@@

  \bibliographystyle{IEEEtran}
  \bibliography{bib/references.bib}
% 	\begin{itemize}
% 		\item T. Xie, H. Jiang, X. Zhao, and C. Zhang, “A wi-fi-based wireless indoor position sensing system with multipath interference mitigation,” Sep 2019. [Online].
% Available: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6767237/
% 		\item A. M. Ladd, K. E. Bekris, A. Rudys, L. E. Kavraki, and D. S. Wallach, “Robotics-
% based location sensing using wireless ethernet,” Wireless Networks, vol. 11, no. 1-2, p. 189–204, 2005.
% 		\item M. Lindhe, K. Johansson, and A. Bicchi, “An experimental study of exploiting multipath fading for robot communications,” Robotics: Science and Systems III, 2007.
% 		\item M. Lindhe and K. Johansson, “Using robot mobility to exploit multipath fading,”Wireless Communications, IEEE, vol. 16, pp. 30 – 37, 03 2009.
% 	\end{itemize}

>>>>

\title[HIL Plant Modeling]{Hardware-in-Loop Plant Modeling for Autonomous
  Vehicle}

% % A subtitle is optional and this may be deleted
\subtitle{Modeling, Simulation, and Testing}

\author[H.~Grady, N.~Nauman]{Hannah~Grady \and Nicholas~Nauman 
\linebreak Advisors:~Dr.~Suruz~Miah}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

\begin{frame}{Introduction}{}
    \begin{block}{Applications of Autonomous Vehicles}
    	\begin{itemize}
    		\item Autonomous vehicles are being developed by many companies for commercial and personal use
    		\item Modeling the steering system for autonomous vehicles is a challenging task
     		\item Models for autonomous vehicle subsystems must be very accurate due to safety factors
		\end{itemize}
    \end{block}
        \begin{figure}
			\centering
			\begin{minipage}[t]{0.4\textwidth}
				\centering
				\includegraphics[height=1.5cm]{figs/img/autonomousVehiclesAStuff}
				\caption{AutonomouStuff Vehicle Fleet\textsuperscript{a}}
				\label{fig:fleet}
			\end{minipage}
			\begin{minipage}[t]{0.4\textwidth}
				\centering
				\includegraphics[height=1.5cm]{figs/img/autonomousVehiclesSteering}
				\caption{Autonomous Vehicle Steering System\textsuperscript{b}}
				\label{fig:steerSystem}
			\end{minipage}
        \end{figure}
    \begin{tiny}
		\textsuperscript{a}https://hexagonpositioning.com/pi-brands/autonomoustuff\\\textsuperscript{b}https://www.autonews.com/article/20181105/OEM10/181109921/delphi-s-pace-award-winning-e-steer-an-autonomous-vehicle-building-block
    \end{tiny}
\end{frame}

\begin{frame}{Problem Statement}
  \begin{block}{Problem Statement}
    \begin{large}
      Model vehicle subsystems for a Lexus platform.
 \begin{itemize}
          \item Steering Model
          \item Acceleration Model
          \item Brake Model
          \item Shift Model
          \item Speed Model
          \item Speed Control Model
        \end{itemize} 
    \end{large}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{large}
      Use conventional System Identification techniques for modeling subsystems based on available raw data.  
    \end{large}
  \end{block}
\end{frame}

@@

\begin{frame}{Literature Review}
  \begin{block}{Existing Solution}
        Use of System Identification Toolbox in Matlab to create models from data~\cite{Donjaroennon2021}
  \end{block}
  \begin{block}{Existing Solution}
        Third order ARMAX model creates models using traditional methods of analysis~\cite{Li1999}
  \end{block}
  \begin{block}{Existing Solution}
        Steer-By-Wire method as a system model~\cite{Saruchi2015}
  \end{block}
    % \begin{figure}[b]
    %     \centering
    %     \includegraphics[width=0.45\textwidth]{figs/img/CompaRob}
    %     \caption{CompaRob}
    %     %\label{fig:sysBlockDiag}
    % \end{figure}
\end{frame}

@@

\begin{frame}{Existing Solutions}
  \begin{block}{Problems}
    \begin{itemize}
      \item Require line-of-sight between robot and user
      \item Some require costly dedicated image processing hardware
    \end{itemize}
  \end{block}
  \pause
  \begin{block}{Benefits of Proposed Solution}
    \begin{itemize}
      \item High level of accuracy 
    \end{itemize}
  \end{block}
\end{frame}

@@

\section{System Requirements}
\begin{frame}{System Requirements}
  \begin{block}{Specifications}
    \begin{itemize}
      	\item The plant model should have an accurate model of the six main subsystems
    		\item A hardware-in-loop (HIL) test bench can be developed from the plant models of the subsystems
    		\item The steering model can handle very small steering angles
    \end{itemize}
  \end{block}
\end{frame}

@@

\section{Concluding Remarks}
\begin{frame}{Concluding Remarks}
  \begin{block}{Project goals}
    \begin{LARGE}
      \begin{itemize}
        \item Develop models of an autonomous vehicle's subsystems
        \begin{itemize}
          \item Steering Model
          \item Acceleration Model
          \item Brake Model
          \item Shift Model
          \item Speed Model
          \item Speed Control Model
        \end{itemize}
      \end{itemize}
    \end{LARGE}
  \end{block}
  \begin{block}{Anticipated Challenges}
    \begin{itemize}
      \item Achieving an acceptable accuracy and reliability for each model due to its nonlinearities over small changes
    \end{itemize}
  \end{block}
\end{frame}

@@

%\begin{frame}{References}
%  \bibliographystyle{IEEEtran}
%   \begin{itemize}
%     \item N. Rawashdeh, R. Haddad, O. Jadallah, and A. To’ma, “A person-following
% robotic cart controlled via a smartphone application: design and evaluation,”
% 09 2017, pp. 1–5.
%     \item M. M. Islam, A. Lam, H. Fukuda, Y. Kobayashi, and Y. Kuno, “An intelligent
% shopping support robot: understanding shopping behavior from 2d skeleton data using gru network,” ROBOMECH Journal, vol. 6, no. 1, 2019.
%     \item J. Sales, J. Marti, R. Marin Prades, E. Cervera, and P. Sanz, “Comparob: The
% shopping cart assistance robot,” International Journal of Distributed Sensor Networks, vol. 2016, pp. 1–15, 02 2016.
%     \item M. S. Miah, J. Knoll, and K. Hevrdejs, “Intelligent range-only mapping and navigation for mobile robots,” IEEE Transactions on Industrial Informatics, vol. 14, no. 3, pp. 1164–1174, 2018.
%     \item D. Li and S. Lane, “A novel and versatile parabolic reflector that significantly
% improves wi-fi reception at different distances and angles,” 2013.

@@

  \bibliographystyle{IEEEtran}
  \bibliography{bib/references.bib}

%\begin{itemize}
%\item
%@INPROCEEDINGS{Donjaroennon2021,
%  author={Donjaroennon, Natthapon and Nuchkum, Suphatchakan and Leeton, Uthen},
%  booktitle={2021 9th International Electrical Engineering Congress (iEECON)}, 
%  title={Mathematical model construction of DC Motor by closed-loop system Identification technique Using Matlab/Simulink}, 
%  year={2021},
%  volume={},
%  number={},
%  pages={289-292},
%  doi={10.1109/iEECON51072.2021.9440305}}
%\end{itemize}
% 	\begin{itemize}
% 		\item T. Xie, H. Jiang, X. Zhao, and C. Zhang, “A wi-fi-based wireless indoor position sensing system with multipath interference mitigation,” Sep 2019. [Online].
% Available: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6767237/
% 		\item A. M. Ladd, K. E. Bekris, A. Rudys, L. E. Kavraki, and D. S. Wallach, “Robotics-
% based location sensing using wireless ethernet,” Wireless Networks, vol. 11, no. 1-2, p. 189–204, 2005.
% 		\item M. Lindhe, K. Johansson, and A. Bicchi, “An experimental study of exploiting multipath fading for robot communications,” Robotics: Science and Systems III, 2007.
% 		\item M. Lindhe and K. Johansson, “Using robot mobility to exploit multipath fading,”Wireless Communications, IEEE, vol. 16, pp. 30 – 37, 03 2009.
% 	\end{itemize}
